Binary companions of red giant stars I: \\ catalog and companions that survive the common envelope phase

### 2017-08-11 paper/1-catalog/twoface-catalog.tex
intro shite

% style notes
% -----------
% - This file generates by Makefile; don't be typing ``pdflatex'' or some
%   bullshit.
% - Line break between sentences to make the git diffs readable.
% - Simple Monte Carlo gets a capital S to indicate that it is a defined thing.
% - Use \, as a multiply operator.
% - Reserve () for function arguments; use [] or {} for outer shit.
% - Always prior pdf or posterior pdf, never prior or posterior (that's your
%   arse).
% - Use \sectionname not Section, \figname not Figure, \documentname not Article
%   or Paper or paper.
% - Make sure that two assumptions in the two assumption lists only have the
%   same name if they really are the same assumption: These are proper names!
% - Hyphenate binary-star when it is an adjective, not when it is a noun!
% - Where there are defined math symbols (like \pars), use them!

% other notes
% - Binary engulfment reference: https://arxiv.org/pdf/1002.2216.pdf

@@

\title{Binary companions of red clump stars I: \\
       catalog and surviving companions}

@@

\begin{abstract}\noindent % trust me
% Context
Repeat radial-velocity measurements of stars can be used to find stellar,
sub-stellar, and planetary companions of stars.
The \apogee\ survey has measured multi-epoch but sparse radial velocities for
$> XX$ (mainly red giant) stars.
Though even few observations are useful for detecting companions, such data are
difficult to use for constraining the physical properties of companions because
permitted orbital solutions are highly degenerate.
% Aims
Here we perform a search for secondary companions of \nRC\ red clump (\RC) and
\nRGB\ red giant branch (\RGB) stars that have similar radii to \RC\ stars
observed as part of the \apogee\ survey.
Because the primary-star masses are known, the mass-function degeneracy is
broken and the secondary-companion masses ($m\,\sin i$) can be inferred.
% Methods
We use a custom-built Monte Carlo sampler (\thejoker) combined with prior
measurements of primary masses and stellar parameters to deliver (often highly
multi-modal) posterior beliefs about companion mass, pericenter distance, and
other orbital parameters for the \RC\ and \RGB\ stars.
% Results
We deliver a catalog of \ncompanions\ companions \todo{that meet some criteria},
and posterior samplings for all \ntotal\ stars in the parent sample.
We find \todo{describe} differences between the companions around \RC\ and \RGB\
stars that are \todo{in/consistent} with the theoretical prediction that
stellar companions should not survive the common-envelope \RGB\ phase.
We additionally find trends with chemical abundances, and we find tentative
evidence for ZZZ and WWW.
\end{abstract}

@@

APW: Opening sentence: Even with one single star and two epochs, if we
see an RV change, there must be binaries! What more can we say? Can we
infer binary populations from bad data?

>>>>

% style notes
% -----------
% - This file generates by Makefile; don't be typing ``pdflatex'' or some BS.
% - Line break between sentences to make the git diffs readable.
% - Use \, as a multiply operator.
% - Reserve () for function arguments; use [] or {} for outer shit.
% - Always prior pdf or posterior pdf, never prior or posterior (that's your
%   arse).
% - Use \sectionname not Section, \figname not Figure, \documentname not Article
%   \tablename not Table, \eqname not Equation.
% - Make sure that two assumptions in the two assumption lists only have the
%   same name if they really are the same assumption: These are proper names!
% - Hyphenate binary-star when it is an adjective, not when it is a noun!
% - Where there are defined math symbols (like \pars), use them!

% other notes
% -----------
% - Binary engulfment reference: https://arxiv.org/pdf/1002.2216.pdf

@@

\title{Binary companions of red giant stars I: \\
       catalog and companions that survive the common envelope phase}

@@

\begin{abstract}\noindent % trust me
% Context
Repeat radial-velocity measurements of stars can be used to find stellar,
sub-stellar, and planetary companions.
The \apogee\ survey (\DR) has measured multi-epoch but sparse radial velocities
for $> XX$ (mainly red giant) stars.
Though even few observations are useful for detecting companions, such data are
difficult to use for constraining the physical properties of companions because
permitted orbital solutions are highly degenerate.
% Aims
Here we perform a search for secondary companions of \nRC\ red clump (\RC) and
\nRGB\ red giant branch (\RGB) stars that have similar radii to \RC\ stars
using data from the \apogee\ survey.
Because the primary-star masses are known, the mass-function degeneracy is
broken and the secondary-companion masses ($m\,\sin i$) can be inferred.
% Methods
We use a custom-built Monte Carlo sampler (\thejoker) combined with prior
measurements of primary masses and stellar parameters to deliver (often highly
multi-modal) posterior beliefs about companion mass, pericenter distance, and
other orbital parameters for the \RC\ and \RGB\ stars.
% Results
We deliver a catalog of \ncompanions\ companions \todo{that meet some criteria},
and posterior samplings for all \ntotal\ stars in the parent sample.
We find \todo{describe} differences between the companions around \RC\ and \RGB\
stars that are \todo{in/consistent} with the theoretical prediction that
stellar companions should not survive the common-envelope \RGB\ phase.
We additionally find trends with chemical abundances, and we find tentative
evidence for ZZZ and WWW.
\end{abstract}

@@

Time-domain radial velocity measurements of stars fundamentally contain
information about massive companions: even with two observations of a single
star, a difference in the measured radial velocities implies the existence of at
least one companion.
Of course with just two observations, the orbital properties of the companion(s)
will be very poorly constrained.
Most prior searches for companions using radial velocity data have therefore
restricted their searches to only stars with ``sufficient'' data where the
orbital solution is unamibiguous under the ... noise model.

Many of the largest (in number of objects) stellar spectroscopic surveys observe
large samples of stars sparsely, non-uniformly, and imprecisely.

Even if period, generic orbital parameters are poorly known, limits on companion
mass or pericenter
